---
title: "Analysis of Results for: *A case study of virtual reality equivalence in a delayed match-to-sample task with a language-trained bonobo (Pan paniscus)*"
author: "Catherine Hallsten"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.height = 4, message = FALSE)

library(tidyverse)
library(fs)
library(readxl)
library(here)
library(parameters)
library(broom)
library(logistf)
library(janitor)
library(patchwork)
library(knitr)
library(slider)

set.seed(2021-05-06)

ex1ex2binom <- list()

test_data <- read_csv(here("exp1_test_extra_data.csv"))%>% 
  mutate(Modality = fct_relevel(Modality, c("Lex", "Pic", "3D")))
```

# Experiment 1

## Section 2.1.1. Overall Accuracy

```{r}
plot_data <- test_data %>% 
  group_by(Modality) %>% 
  nest() %>% 
  ungroup() %>% 
  rename(DF = data) %>% 
  mutate(binom_test = map(DF, ~ binom.test(sum(.x$Correctness), length(.x$Correctness)))) %>% 
  mutate(binom_test = map(binom_test, tidy)) %>% 
  unnest(binom_test) %>% 
  select(-DF, -method, -alternative, -statistic, -parameter)

ex1ex2binom[[1]] <- plot_data %>% 
  mutate(Experiment = 1)

plot_data %>% kable()
```

### Figure 8

```{r}
plot_data %>% 
  rename(Accuracy = estimate) %>% 
  ggplot(aes(Modality, Accuracy)) +
  geom_col(fill =  scales::hue_pal()(3)) + 
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .25)
```

## Section 2.1.2.	First Trial Accuracy

```{r}
fts <- read_xlsx(here("first-trial-success.xlsx")) 

fts1_tbl <- tribble(
  ~Correct, ~Total, ~"p-Value",
  fts %>% 
    slice(1:6) %>%
    pull(Correctness) %>% sum(), 
  fts %>% 
    slice(1:6) %>%
    pull(Correctness) %>% 
    length(),
  fts %>% 
    slice(1:6) %>%
    pull(Correctness) %>% 
    {binom.test(sum(.), length(.))} %>% 
    .$p.value
)

fts2_tbl <- tribble(
  ~Correct, ~Total, ~"p-Value",
  fts %>% 
    pull(Correctness) %>% sum(), 
  fts %>% 
    pull(Correctness) %>% length(),
  fts %>% 
    pull(Correctness) %>% 
    {binom.test(sum(.), length(.))} %>% 
    .$p.value
)
```

first-trial accuracy for each first pair exposure:

```{r}
fts1_tbl %>% kable()
```

first trial accuracy for each matching word:

```{r}
fts2_tbl %>% kable()
```

## 2.1.3.	Accuracy Compared Across Conditions

### Table 1

```{r}
(modality_model <- logistf(Correctness ~ Modality, data = test_data, family = "binomial")) %>% 
  parameters::parameters(exponentiate = TRUE) %>% 
  select(-CI, -df_error) %>% 
  kable()
```

likelihood ratio test comparing this model to a null model: 

```{r}
null_model <- logistf(Correctness ~ 1, data = test_data, family = "binomial")
lrt <- anova(null_model, modality_model)
tribble(~"Chi-Squared", ~DF, ~"p-Value", lrt$chisq, lrt$df, lrt$pval) %>% 
  kable()
```

### Table 2

```{r}
(pic.firth <- test_data %>% 
  mutate(Modality = fct_relevel(Modality, c("Pic", "Lex", "3D"))) %>% 
    logistf(Correctness ~ Modality, data = ., family = "binomial") %>% 
    parameters(exponentiate = TRUE)) %>% 
  select(-CI, -df_error) %>% 
  kable()
```

## 2.1.4.	Accuracy over Time

```{r}
test_data %>% 
  group_by(Modality) %>% 
  mutate(TTN = 1:n()) %>%
  nest() %>% 
  ungroup() %>% 
  rename(DF = data) %>% 
  mutate(GLM = map(DF, ~ glm(Correctness ~ TTN, data = .x, family = "binomial"))) %>% 
  mutate(GLM = map(GLM, parameters, exponentiate = TRUE)) %>% 
  unnest(GLM) %>% 
  select(-DF, -CI, -df_error) %>% 
  kable(digits = 5)
```

### Figure 9

```{r}
p1 <- test_data %>% 
  group_by(Modality) %>%
  mutate(TTN = 1:n()) %>% 
  ungroup() %>% 
  filter(Modality == "Lex") %>%
  mutate(Correctness = as.numeric(Correctness)) %>%
  mutate(Correctness_ = slide_mean(Correctness, before = Inf)) %>% 
  ggplot(aes(x = TTN, y = Correctness_ )) + 
  geom_line(color = "blue") +
  geom_point(aes(x = TTN, y = Correctness), color = "black", size = 1.5, shape = 1) +
  xlab("Total Trial Number (Lexigram)") +
  ylab("Accuracy") +
  ylim(0, 1) +
  theme_update(plot.title = element_text(hjust = 0.5))

p2 <- test_data %>% 
  group_by(Modality) %>%
  mutate(TTN = 1:n()) %>% 
  ungroup() %>% 
  filter(Modality == "3D") %>%
  mutate(Correctness = as.numeric(Correctness)) %>%
  mutate(Correctness_ = slide_mean(Correctness, before = Inf)) %>%
  ggplot(aes(x = TTN, y = Correctness_ )) + 
  geom_line(color = "blue") +
  geom_point(aes(x = TTN, y = Correctness), color = "black", size = 1.5, shape = 1) +
  xlab("Total Trial Number (3D-Object)") +
  ylab("Accuracy") +
  ylim(0, 1) +
  theme_update(plot.title = element_text(hjust = 0.5))

p1 + p2
```

## 2.1.5.	Latency over Time 

```{r}
test_data %>% 
  group_by(Modality) %>% 
  mutate(TTN = 1:n()) %>%
  ungroup() %>% 
  mutate(Correctness = as.numeric(Correctness)) %>% 
  filter(Correctness > 0) %>% 
  group_by(Modality) %>% 
  nest() %>% 
  ungroup() %>% 
  rename(DF = data) %>% 
  mutate(LM = map(DF, ~ lm(Seconds ~ TTN, data = .x))) %>% 
  mutate(LM = map(LM, parameters)) %>% 
  unnest(LM) %>% 
  select(-DF, -df_error, -CI) %>% 
  kable()
```

### Figure 10

```{r}
test_data %>% 
  group_by(Modality) %>% 
  mutate(TTN = 1:n()) %>%
  ungroup() %>%
  mutate(Correctness = as.numeric(Correctness)) %>% 
  filter(Correctness > 0) %>% 
  mutate(Modality = case_when(
    Modality == "Lex" ~ "Lexigram",
    Modality == "Pic" ~ "Photo",
    Modality == "3D" ~ "3D-Object"
  )) %>%
  mutate(Modality = fct_relevel(Modality, c("Lexigram", "Photo", "3D-Object"))) %>% 
  ggplot(aes(TTN, Seconds, color = Modality)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Total Trial Number") +
  ylim(0, 9)
```

# Experiment 2

```{r}
set.seed(2021-05-06)

test_data <- read_csv(here("exp2_test_data.csv")) %>% 
  mutate(Modality = fct_relevel(Modality, c("Lex", "Pic", "3D")))
```

## 2.2.1.	Overall Accuracy

```{r}
plot_data <- test_data %>% 
  group_by(Modality) %>% 
  nest() %>% 
  ungroup() %>% 
  rename(DF = data) %>% 
  mutate(binom_test = map(DF, ~ binom.test(sum(.x$Correctness), length(.x$Correctness)))) %>% 
  mutate(binom_test = map(binom_test, tidy)) %>% 
  unnest(binom_test) %>% 
  select(-DF, -method, -alternative, -statistic, -parameter)

ex1ex2binom[[2]] <- plot_data %>% 
  mutate(Experiment = 2)

ex1ex2binom <- ex1ex2binom %>% bind_rows()

plot_data %>% kable()
```

### Figure 11

```{r}
plot_data %>% 
  rename(Accuracy = estimate) %>% 
  ggplot(aes(Modality, Accuracy)) +
  geom_col(fill =  scales::hue_pal()(3)) + 
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = .25)
```

## 2.2.2.	First Trial Accuracy

```{r}
fts <- read_xlsx(here("first-trial-success-exp-2.xlsx")) 

fts1_tbl <- tribble(
  ~Correct, ~Total, ~"p-Value",
  fts %>% 
    slice(1:6) %>%
    pull(Correctness) %>% sum(), 
  fts %>% 
    slice(1:6) %>%
    pull(Correctness) %>% 
    length(),
  fts %>% 
    slice(1:6) %>%
    pull(Correctness) %>% 
    {binom.test(sum(.), length(.))} %>% 
    .$p.value
)

fts2_tbl <- tribble(
  ~Correct, ~Total, ~"p-Value",
  fts %>% 
    pull(Correctness) %>% sum(), 
  fts %>% 
    pull(Correctness) %>% length(),
  fts %>% 
    pull(Correctness) %>% 
    {binom.test(sum(.), length(.))} %>% 
    .$p.value
)
```

first-trial accuracy for each first pair exposure:

```{r}
fts1_tbl %>% kable()
```

first trial accuracy for each matching word:

```{r}
fts2_tbl %>% kable()
```

## 2.2.3.	Accuracy Compared Across Conditions

### Table 3

```{r}
(modality_model <- glm(Correctness ~ Modality, data = test_data, family = "binomial")) %>% 
  parameters(exponentiate = TRUE) %>% 
  select(-CI, -df_error) %>% 
  kable()
```

likelihood ratio test comparing this model to a null model: 

```{r}
null_model <- glm(Correctness ~ 1, data = test_data, family = "binomial")
lrt <- anova(null_model, modality_model, test = "LRT")
tribble(~"Chi-Squared", ~DF, ~"p-Value", lrt$Deviance[2], lrt$Df[2], lrt$`Pr(>Chi)`[2]) %>% 
  kable()
```

### Table 4

```{r}
(pic_exp2 <- test_data %>% 
  mutate(Modality = fct_relevel(Modality, c("Pic", "Lex", "3D"))) %>% 
    glm(Correctness ~ Modality, data = ., family = "binomial") %>% 
    parameters(exponentiate = TRUE)) %>% 
  select(-CI, -df_error) %>% 
  kable()
```

## 2.2.4.	Accuracy Over Time

```{r}
test_data %>% 
  group_by(Modality) %>% 
  mutate(TTN = 1:n()) %>%
  nest() %>% 
  ungroup() %>% 
  rename(DF = data) %>% 
  mutate(GLM = map(DF, ~ glm(Correctness ~ TTN, data = .x, family = "binomial"))) %>% 
  mutate(GLM = map(GLM, parameters, exponentiate = TRUE)) %>% 
  unnest(GLM) %>% 
  select(-DF) %>% 
  select(-CI, -df_error) %>% 
  kable(digits = 5)
```

### Figure 12

```{r}
p1 <- test_data %>% 
  group_by(Modality) %>%
  mutate(TTN = 1:n()) %>% 
  ungroup() %>% 
  filter(Modality == "Lex") %>%
  mutate(Correctness = as.numeric(Correctness)) %>%
  mutate(Correctness_ = slide_mean(Correctness, before = Inf)) %>% 
  ggplot(aes(x = TTN, y = Correctness_ )) + 
  geom_line(color = "blue") +
  geom_point(aes(x = TTN, y = Correctness), color = "black", size = 1.5, shape = 1) +
  xlab("Total Trial Number (Lexigram)") +
  ylab("Accuracy") +
  ylim(0, 1) +
  theme_update(plot.title = element_text(hjust = 0.5))

p2 <- test_data %>% 
  group_by(Modality) %>%
  mutate(TTN = 1:n()) %>% 
  ungroup() %>% 
  filter(Modality == "Pic") %>%
  mutate(Correctness = as.numeric(Correctness)) %>%
  mutate(Correctness_ = slide_mean(Correctness, before = Inf)) %>%
  ggplot(aes(x = TTN, y = Correctness_ )) + 
  geom_line(color = "blue") +
  geom_point(aes(x = TTN, y = Correctness), color = "black", size = 1.5, shape = 1) +
  xlab("Total Trial Number (Photo)") +
  ylab("Accuracy") +
  ylim(0, 1) +
  theme_update(plot.title = element_text(hjust = 0.5))

p3 <- test_data %>% 
  group_by(Modality) %>%
  mutate(TTN = 1:n()) %>% 
  ungroup() %>% 
  filter(Modality == "3D") %>%
  mutate(Correctness = as.numeric(Correctness)) %>%
  mutate(Correctness_ = slide_mean(Correctness, before = Inf)) %>%
  ggplot(aes(x = TTN, y = Correctness_ )) + 
  geom_line(color = "blue") +
  geom_point(aes(x = TTN, y = Correctness), color = "black", size = 1.5, shape = 1) +
  xlab("Total Trial Number (3D-Object)") +
  ylab("Accuracy") +
  ylim(0, 1) +
  theme_update(plot.title = element_text(hjust = 0.5))


p4 <- ggplot() + theme_void() 

(p2 + p3) /
(p1 + p4)
```

## 2.2.5.	Latency Over Time

```{r}
test_data %>% 
  group_by(Modality) %>% 
  mutate(TTN = 1:n()) %>%
  ungroup() %>% 
  mutate(Correctness = as.numeric(Correctness)) %>% 
  filter(Correctness > 0) %>% 
  group_by(Modality) %>% 
  nest() %>% 
  ungroup() %>% 
  rename(DF = data) %>% 
  mutate(LM = map(DF, ~ lm(Seconds ~ TTN, data = .x))) %>% 
  mutate(LM = map(LM, parameters)) %>% 
  unnest(LM) %>% 
  select(-DF, -df_error, -CI) %>% 
  kable()
```

### Figure 13

```{r}
test_data %>% 
  group_by(Modality) %>% 
  mutate(TTN = 1:n()) %>%
  ungroup() %>%
  mutate(Correctness = as.numeric(Correctness)) %>% 
  filter(Correctness > 0) %>% 
  mutate(Modality = case_when(
    Modality == "Lex" ~ "Lexigram",
    Modality == "Pic" ~ "Photo",
    Modality == "3D" ~ "3D-Object"
  )) %>%
  mutate(Modality = fct_relevel(Modality, c("Lexigram", "Photo", "3D-Object"))) %>% 
  ggplot(aes(TTN, Seconds, color = Modality)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Total Trial Number") +
  ylim(0, 9)
```

# 2.3. Comparison of Experiment 1 and Experiment 2 Accuracy

```{r}
ex1ex2binom %>% 
  mutate(Experiment = as.character(Experiment)) %>% 
  mutate(Modality = case_when(
    Modality == "Lex" ~ "Lexigram",
    Modality == "Pic" ~ "Photo",
    Modality == "3D" ~ "3D-Object"
  )) %>%
  mutate(Modality = fct_relevel(Modality, c("Lexigram", "Photo", "3D-Object"))) %>% 
  ggplot(aes(fct_inorder(Modality), estimate, fill = Experiment)) +
  geom_bar(position = "dodge", stat="identity") +
  labs(x = "Modality", y = "Accuracy") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  geom_hline(yintercept = 0.50, linetype = 2, size = 0.75)
```

\newpage

# Session Info

```{r}
sessionInfo()
```